NumPy---Array Computation for Python

### 2019-12-10 paper.tex
Add impact now

% Packages
\usepackage{pifont}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{float}
% \usepackage[multiple]{footmisc}
\usepackage{booktabs}
\usepackage{csquotes}
\usepackage{listings, textcomp}

@@

>>>>

% Packages
\usepackage{pifont}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{float}
% \usepackage[multiple]{footmisc}
\usepackage{booktabs}
\usepackage{csquotes}
\usepackage{listings, textcomp}
\lstset{language=Python}

@@

\subsection*{Conclusion}

\subsubsection*{Impact Now}

NumPy, while having been wildly successful as a library and array
exchange project, has now also become a standard language for expressing array
and tensor computations.  For example, the NumPy API is implemented by
several popular tensor computation libraries including CuPy
(https://cupy.chainer.org/), Jax
(https://jax.readthedocs.io/en/latest/jax.numpy.html), PyTorch
(https://pytorch.org/tutorials/beginner/blitz/tensor\_tutorial.html),
and Apache MXNet
(https://mxnet.incubator.apache.org/api/python/docs/api/ndarray/index.html),
and to a lesser extent TensorFlow
(https://www.tensorflow.org/api\_docs/python/tf/Tensor).

Another notable example is Dask, a library for parallel computing in
Python.  Dask adopts the NumPy API and therefore presents a familiar
interface to existing NumPy users, while adding powerful abilities to
parallelize and distribute tasks.

In order to aid better interaction between NumPy and these libraries,
an ``array function'' protocol was added to NumPy in 2018 (see Section
X). The new protocol allows for external array objects (sometimes
called ``duck arrays'') to pass through NumPy:

\begin{lstlisting}
  import numpy as np
  import cupy as cp

  x_gpu = cp.array([1, 2, 3])
  y = np.sum(x_gpu)  # This works, and returns a GPU array
\end{lstlisting}

\subsubsection*{Future Development}
